analysis

### 2022-10-24 r-analysis/analysis.Rmd
bugfix

source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)

>>>>

source("r-analysis/per_capita_emissions_china_and_regions", local = TRUE, print.eval = TRUE)
source("r-plots/plot_bar_per_capita_emissions_2019", local = TRUE, print.eval = TRUE)
